Dissertation draft

### 2023-07-16 Texfiles/Draft1.tex
end of day

I first solve a modified retirement lifecycle model. The problem that retirees face is as follows:
\textbf{This is not correct -- need to include probs}
\begin{equation*}
      E(U) = \sum_{t = x}^{110 - w}[u(c_{t})]
\end{equation*}
subject to their budget constraint
\begin{equation*}
      c_{t} =a_{t}(1 +r) + p_{t} + ann_{t} -  a_{t+1}
\end{equation*}
where $a_{t}$ are asset holdings in time t, $p_{t}$ is state pension income in time t, and $ann_{t}$ is annuity
income in time t. I use the standard CRRA utility function.
\begin{equation*}
      u(c_{t}) = \frac{c_{t}^{1 - \sigma}}{1 - \sigma}
\end{equation*} In some specifications retirees can leave bequests, I use the bequest function from
\cite{lockwood_red_2012}.
\begin{equation*}
      u(b_{t}) = (\frac{m}{1 - m})^{\sigma}  \frac{((\frac{m c_{0}}{1 - m}) + b_{t})^(1 - \sigma)}{(1 - \sigma)}
\end{equation*}
Where $b_{t}$ is the amount left at death, $m$ is a measure of bequest motive strength and $c_{0}$ is
a minimum amount of consumption that individuals want. \textbf{Check this}

@@

To simulate the ELSA data I solve this retirement problems for each new retiree in the data set.

>>>>

I first solve a modified retirement lifecycle model. The problem that retirees face is as follows:
\textbf{This is not correct -- need to include probs}
\begin{equation*}
      E(U) = \sum_{t = x}^{110 - w}[u(c_{t})]
\end{equation*}
subject to their budget constraint
\begin{equation*}
      c_{t} =a_{t}(1 +r) -  a_{t+1} + y_{t}
\end{equation*}
where $a_{t}$ are asset holdings in time t and $y_{t}$ is income in period 2. Income can come either
from state pensions, defined benefit pension plans or purchased annuities.
\begin{equation*}
      u(c_{t}) = \frac{c_{t}^{1 - \sigma}}{1 - \sigma}
\end{equation*} In some specifications retirees can leave bequests, I use the bequest function from
\cite{lockwood_red_2012}.
\begin{equation*}
      u(b_{t}) = (\frac{m}{1 - m})^{\sigma}  \frac{((\frac{m c_{0}}{1 - m}) + b_{t})^(1 - \sigma)}{(1 - \sigma)}
\end{equation*}
Where $b_{t}$ is the amount left at death, $m$ is a measure of bequest motive strength and $c_{0}$ is
a minimum amount of consumption that individuals want. \textbf{Check this}

@@

To simulate the ELSA data I solve this retirement problems for each new retiree in the data set dependent on their
objective probability of death each period. I estimate with subjective life expectancies and objective life expectancies,
I also estimate the model both with and without a bequest motive which was picked to fit the unforced real annuity
rates seen in the data. I then estimate several empirical models with the simulated data.

\subsection{Empirical models}

In this section I outline the key empirical models I run with both the simulated consumption data from the
lifecycle models and with the real data from ELSA. I then see which lifecycle model better fits the consumption
response that happened as a result of the pension reform.

I use a regression discontinuity design where I compare the consumption of recent retirees after the policy reform
to recent retirees before the policy reform. The individuals who retired in 2014 and later were not forced to
annuitise their defined contribution pension. The key assumption implicit in regression discontinuities is
that nothing else changes at the time of the jump apart from the policy of interest. And that the policy occurs
without individuals predicting it. The policy change was widely seen as a surprise by the media and financial planners,
some of whom in fact complained that they had not been consulted enough. \textbf{How can I justify no other jumps at the jump}

Retirement year is the running variable and individuals are treated if retirement year is greater than 2013 and less than 2016.
I consumption of individuals up to 2 years into retirement so that the sample size is larger. So if someone retired in 2014 and
had consumption data in 2014 and 2016 I include both values. An individual is considered not treated if they retire before 2013 and after 2011.

The estimating equation is therefore
